---
title: "Course Project : writeup"
author: "samrudha kelkar"
date: "Sunday, October 26, 2014"
output: html_document
---

This is my submission towards Coursera Course on "Practical Machine Leraning" conducted by John Hopkins Bloomberg School of Public Health in Oct-Nov 2014

Training Model:

With the available training and testing data, I used **Random forest** method to train the model. I considered following things:

1.Predictors present in testing data

2.Typically "sufficient" sensors used in motion prediction
   + Gyrometer and accerometer data would be sufficient to train the model
   
3.Variance of the predictors

Pre-processing:

I used **PCA** method for preprocessing considering the large number of original predictors.
*pcaComp factor* is chosen such that most of the variations are covered.


Summary of the model:
```{r, echo=FALSE, background= '#8B0000'}
ModelFit3

```


Confusion matrix thus generated is as follows:
```{r, echo=FALSE, background= '#8B0000'}
 library(caret)
 confusionMatrix(PredictionDummy5,testingDummy$classe)
```

It is said that Boosting combined with random forest produce better results. 

I used information provided by boosting model about variance of predictors. Considering only high "informative" predictors I built another model.

Computation of this model was fast as lesser predictors were involved and accuracy was improved.

```{r, echo=FALSE , background= '#FAF0E6'}
library(caret)
confusionMatrix(PredictionDummy6,testingDummy$classe)
ModelFit6

```


One of the characteristic observation is that totalAccelArm is always <50 for classe "A":
![alt text][1]

[1]:C:\Users\Sam\Study\PracticalMachineLearning\AssinmentSubmission/AccelArm.png "Class A versus Accleration"

